Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia

### 2013-11-03 article/article-draft.tex
Added count of non-template sentences to template scoring code

After applying the score to the entire set of wiki clusters (with a score threshold of .6), I get 122,698 template clusters and 268,433 non-template clusters. The template clusters contain 777,940 sentences (689743 unique) and the non-template 698,628 (400,458 unique).

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{classifyscoreswiki.pdf}
\caption{Histogram of Hand Labeled Clusters by Template Heuristic Score.}
\label{heuristic}
\end{figure}

>>>>

N lines: 3496074
N clusters: 1151620
N identical clusters: 666212
N template clusters: 55430
N other clusters: 20745
N other pair clusters: 407963
N species clusters: 1270

N lines: 3496074
N clusters: 1151620
N identical clusters: 666212
N template clusters: 244660
N template sentences: 1116932
N other clusters: 20745
N other pair clusters: 218840
N species clusters: 1163
^C

After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters. The template clusters contain 1,116,932, and the non-template

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{classifyscoreswikinew.pdf}
\caption{Histogram of Hand Labeled Clusters by Template Heuristic Score.}
\label{heuristic}
\end{figure}
